Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-16 docs/paper/paper.tex
Improvements for ways of passing functions

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Functions}\label{sub-sec:functions}
The library must handle the distribution of the code between the different workers when an operation is executed. This is a challenging problem with a lot of possible alternatives \cite{cloud-haskell} \cite{distributed-scheme}.

@@

Considering the fact that \verb+Function+ objects cannot be directly transferred a different serialization approach is to be considered (Sec.~\ref{sub-sec:context} proposes a solution to sharing additional data and functions between the UI thread and workers) a possible alternative is to:
\begin{enumerate}
  \item Serialize the \verb+Function+ to a \verb+String+.
  \item Transfer the \verb+String+ to the worker.
  \item Create a new \verb+Function+ on the worker from that \verb+String+.
\end{enumerate}

@@

>>>>

@@

\subsection{Functions}\label{sub-sec:functions}
The library must handle the distribution of the code between the different workers when an operation is executed. This is a challenging problem with many possible alternatives: Cloud Haskell \cite{cloud-haskell} for example, requires a customized version of the Glasgow Haskell Compiler (GHC) to serialize closures and their captured variables as a code pointer and an environment, operating under the assumption that the same code is executed in all nodes. A proposal for using Scheme for distributed programming \cite{distributed-scheme} uses a custom serializable data structure to represent procedures, and macros in order to capture a closure's captured variables and serialize their values. It also assumes that all nodes are executing the same program since serialized functions store pointers to parts of source code files.

In our case, modifying the runtime is not a viable alternative since we want our library to be usable by anyone creating applications for major browser versions.

@@

Considering the fact that \verb+Function+ objects cannot be directly transferred a different serialization approach is to be considered a possible alternative is to:
\begin{enumerate}
  \item Serialize the \verb+Function+ to a \verb+String+.
  \item Transfer the \verb+String+ to the worker.
  \item Create a new \verb+Function+ on the worker from that \verb+String+.
\end{enumerate}

Sec.~\ref{sub-sec:context} proposes a solution to sharing additional data and functions between the UI thread and Web Workers as a replacement for variables captured by closures.

@@

One alternative to hide the \emph{context} concept from application developers could be to introduce a \textit{build} step that detects the variables captured by p-j-s callbacks and transforms the code. By doing this, theyg wouldn't need to do anything out of the ordinary with regards to closures and their environment when working with p-j-s. However, this approach would require transforming the original code, and would be complex and time consuming to implement.
